Commutative character sheaves and geometric types for supercuspidal representations

### 2017-08-04 Geometric types.tex
Adding tilde{L}

If $G$ is nonabelian or disconnected, a similar strategy sometimes succeeds in geometrizing characters $\chi : G(k) \to \EEx$.
Suppose that $G(k) \subset \image(L)$ (which will hold if $G$ is connected).  Then we may associate to each $\chi$ a function $\tilde{\chi}$ as follows.
If $x \in G(k)$, write $x = L(y) = y^{-1}\Frob{G}(y)$ and define $\tilde{\chi}(x) = \chi(\Frob{G}(y) y^{-1})$.
Note that $\tilde{\chi}$ is well defined since changing to $y$ to $gy$ for $g \in G(k)$ has the
effect of conjugating $\Frob{G}(y) y^{-1}$ by $g$, which has no effect on the value of $\chi(\Frob{G}(y) y^{-1})$.
Our second assumption required to geometrize $\chi$ is that $\tilde{\chi}$ is also a character.

>>>>

If $G$ is nonabelian or disconnected, a similar strategy sometimes succeeds in geometrizing characters $\chi : G(k) \to \EEx$.
Suppose that $G(k) \subset \image(L)$ (which will hold if $G$ is connected).  Then we may associate to each $\chi$ a function $\tilde{\chi}$ as follows.
Define $\tilde{L} : G \to G$ by $\tilde{L}(y) = \Frob{G}(y)y^{-1}$.
If $x \in G(k)$, write $x = L(y) = y^{-1}\Frob{G}(y)$ and define $\tilde{\chi}(x) = \chi(\tilde{L}(y))$.
Note that $\tilde{\chi}$ is well defined since changing $y$ to $gy$ for $g \in G(k)$ has the
effect of conjugating $\tilde{L}(y)$ by $g$, which has no effect on the value $\chi(\tilde{L}(y))$.
Our second assumption required to geometrize $\chi$ is that $\tilde{\chi}$ is also a character.
